Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-17 ms.qmd
Fixed up predcition code

######################################################################
# Model predcitions for terrestrial, marine and freshwater ectotherms
######################################################################
# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.

@@

#############################
## Marine ectotherms  
#############################
  marine_data <- sub_data  %>% filter(habitat == "m")
    new_data_m <- data.frame(
      spp = marine_data$spp,
      trait = marine_data$trait,
      habitat = marine_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = marine_data$lat.y,
      long = marine_data$long.x
    )

marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = FALSE)

#############################
## Freshwater ectotherms
#############################
  fresh_data <- sub_data  %>% filter(habitat == "f")
    new_data_f <- data.frame(
      spp = fresh_data$spp,
      trait = fresh_data$trait,
      habitat = fresh_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = fresh_data$lat.y,
      long = fresh_data$long.x
    )

fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = FALSE)

>>>>

######################################################################
# Model predictions for terrestrial, marine and freshwater ectotherms
######################################################################
# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.

@@

#############################
## Marine ectotherms  
#############################
  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, lat.y, long.x)

  new_data_m <- data.frame(
      c_accl_time = 0,
      V = 0,
      trait = 0,
      obs = 0, 
      record_num = 0
    )

  # Create new dataframe with only unique values for predcition.
  new_data_m  <- cbind(marine_data, new_data_m)

  # We'll now make the predcitions from the model object using the new dataframe
  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")

#############################
## Freshwater ectotherms
#############################
  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, lat.y, long.x)

  new_data_f <- data.frame(
      c_accl_time = 0,
      V = 0,
      trait = 0,
      obs = 0, 
      record_num = 0
    )

  # Create new dataframe with only unique values for predcition.
  new_data_f  <- cbind(fresh_data, new_data_f)

  # We'll now make the predcitions from the model object using the new dataframe
  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
